---
title: "Visualize Quantitative Matrix"
author: "UZH n UU -> what shall we use here for authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2: default
  bookdown::pdf_document2: default
bibliography: bibliography.bib
---

```{r load libraries, include=FALSE}
library(readr)
library(heatmap3)
```


```{r load data, eval=TRUE, include=FALSE}
fN <- "qmat_1198.txt"
dat <- read_tsv(fN)
```



# Visualize Using Heatmap3

We are using `r fN` here to visualize these values as a heatmap. We will do this on raw linear values as well as on $\log_{2}$ transformed values.


```{r hmNoTrafo, fig.height=8, fig.width=8, fig.cap="(ref:hmNoTrafo)", eval=TRUE}
heatmap3(as.matrix(dat[,2:ncol(dat)]), na.rm = TRUE, margins = c(10,3))
```
(ref:hmNoTrafo) Shown is the visualization of the quantitative matrix as a heatmap (used here are the linear values)


Now using $\log_{2}$ transformed values it should actually look better.


```{r hmlg2Trafo, fig.height=8, fig.width=8, fig.cap="(ref:hmNoTrafo)", eval=TRUE}
heatmap3(as.matrix(log2(dat[,2:ncol(dat)])), na.rm = TRUE, margins = c(10,3))
```
(ref:hmlg2Trafo) Shown is the visualization of the quantitative matrix as a heatmap using $\log_{2}$ transformed values

